{ \centering Scientific Report - Summary of Research\\ ~\\ Automatized compilation of sequential software to a diverse set of hardware accelerators\\ } ~\\ \vspace{18em} \large Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
Make report oneside
deploy: 8416320dd7f6741afdc2a132465840fdf0ef1113
WIP

\ifx\paperversion\paperversioncamera
  \documentclass[11pt, manuscript, nonacm, natbib]{acmart}\settopmatter{}
\fi

\usepackage{colortbl}

@@

\begin{enumerate}
\item Fast, robust, and correct polyhedral libraries
\item Solid polyhedral compiler infrastructure
\begin{itemize}
\item  Modular pattern-based optimizations for CPU and GPU systems
\item 
DeLICM: Scalar dependence removal
\end{itemize}
\item Fast GPU code generation for climate models
\end{enumerate}

@@

The central components of this library have already been upstreamed into the
open-source LLVM/MLIR project and are usable by the wider research and 
industrial community.

The work in this subproject has been published in \citet{grosser2020fast} and
\citet{pichanatan2021}.

\subsection{Fast GPU code generation for climate models}

@@

The GPU backend of the open-earth compiler has already been upstreamed into
the open-source LLVM/MLIR project and is useable by the wider research
and industrial community.

The work in this subproject has been published in \citet{gysi2020ooc}

>>>>

\ifx\paperversion\paperversioncamera
  \documentclass[11pt, manuscript, nonacm, natbib, oneside]{acmart}\settopmatter{}
\fi

\geometry{twoside=false}
\usepackage{colortbl}

@@

\begin{enumerate}
\item Fast, robust, and correct polyhedral libraries
\item Solid polyhedral compiler infrastructure
\begin{itemize}
\item  Modular pattern-based optimizations for CPU and GPU systems
\item 
DeLICM: Scalar dependence removal
\end{itemize}
\item Fast GPU code generation demonstrated via a climate DSL
\item Code Generation for Emerging Architectures and FPGA
\end{enumerate}

@@

The central components of this library have already been upstreamed into the
open-source LLVM/MLIR project and are usable by the wider research and 
industrial community. The work in this subproject has been published in \citet{grosser2020fast} and
\citet{pichanatan2021}.

\subsection{Fast GPU code generation demonstrated via a climate DSL}

@@

The GPU backend of the open-earth compiler has already been upstreamed into
the open-source LLVM/MLIR project and is useable by the wider research
and industrial community. The work in this subproject has been published in \citet{gysi2020ooc}

\subsection{Code Generation for Emerging Architectures and FPGA}

Automatic optimization for emerging architectures and FPGA has been a principal
objective of this work. We exploited the polyhedral techniques we developed in
earlier tasks to generate high-performance code for emerging memory
architectures such as racetrack memories to optimize polyhedral loop nests and
deep neural networks. We also proposed infrastructure for an open-source
hardware stack that allows for the compilation and simulation of System Verilog
code. We also observed an increased use of systems with where the data models
(e.g., pointer sizes) differ between host systems and accelerators. To ensure
the automatic code generation for such architectures that also allows for
automatic data movement, we expanded LLVM and its OpenMP software stack to
support mixed-data-model offloading.

The LLHD compiler has been upstreamed as open-source into the LLVM/CIRCT
project. The work in this subproject has been published in \citet{khan2020polyhedral},
\citet{schueki2020llhd}, \citet{kurth2020mixed}, and \citet{kourtis2020compiling}.
